### 2018-04-15 tex/paper.tex
Some updates to section 5

This means that we require participants to commit money to cover all possible expenditure \emph{in advance of the contract executing}. In order to make sure that player continue to engage with a contract we ensure urgency by imposing timeouts: money is committed for a finite period, for example, and when waiting for a player to make a commitment we also impose a timeout to ensure that the contract does not become stuck even if one or more of the participants stops interacting with it.

@@

In this section, we show how Marlowe can be used for designing a contract that incentivises saving. We use the 
following example: ``participant 2'' offers 20 ADA to ``participant 1'' in exchange for saving 100 ADA for 100 blocks. 
``Participant 1'' will be able to withdraw the savings after block 20, but if that option is chosen, then ``participant 
2'' will not pay the extra 20 ADA to ``participant 1''.

We will start from outer to inner primitives. The first thing is to allow ``participant 1'' to commit the 100 ADA. The 
primitive says that with identity \haskellinline{IdentCC 1} (this is the identity of the commitment), ``participant 
\haskellinline{1}'' can commit \haskellinline{100} ADA before block \haskellinline{10}, and the commitment must 
expire on block \haskellinline{200}. But if the money is not committed before block \haskellinline{10}, then the 
contract will continue as \haskellinline{Null}.

@@

If the commitment is done correctly and on time, we continue as in \haskellinline{step2}. \haskellinline{step2} is 
another commitment, this time by ``participant 2''. The primitive says that with identity \haskellinline{IdentCC 2},
``participant \haskellinline{2}'' can commit \haskellinline{20} ADA before block \haskellinline{20}, and the commitment
must expire on block \haskellinline{200}. But if the money is not committed before block \haskellinline{20}, then the
contract will continue as \haskellinline{RedeemCC (IdentCC 1) Null}, which in turn gives ``participant 1'' the 
opportunity to withdraw all the money committed immediately.

@@

If the commitment is done correctly and on time, we continue as in \haskellinline{step3}. \haskellinline{step3}
waits until choice with identity \haskellinline{IdentChoice 1} is made by ``participant \haskellinline{1}'' or
until block \haskellinline{100} (whatever happens first). If the choice is made before block \haskellinline{100}, 
it continues as \haskellinline{stepRedeem}, if block \haskellinline{100} comes first, then it continues as 
\haskellinline{step4}.

@@

\haskellinline{step4} pays the \haskellinline{20} ADA committed by ``participant \haskellinline{2}'' in the commit with 
identity \haskellinline{IdentPay 1} to ``participant \haskellinline{1}'', if the payment is claimed before block 
\haskellinline{200}. Once the payment is claimed or after block 200, it continues as \haskellinline{stepRedeem}.

@@

In this section, we give an example of how we can have Marlowe contracts that are easier to write, read, and 
understand, by embedding them into Haskel code (taking advantage that Marlowe contracts are implemented as Haskell 
terms).

The example contract we use through this section implements an escrow contract. Let us imagine that ``participant 1'' 
is buying some item from ``participant 2''. On one hand, if ``participant 1'' pays before receiving the item, there 
is a risk that ``participant 2'' will never give ``participant 1'' the item. On the other hand, if ``participant 2'' 
gives ``participant 1'' the item before ``participant 1'' pays, then there is a risk that ``participant 1'' will never 
pay.

The escrow mechanism allows ``participant 1'' to deposit the money into a contract, in a way that the money will only 
be released when two out of three participants agree on whether ``participant 2'' has indeed given ``participant 1'' 
the item. The third participant (``participant 3'') is supposed to be a neutral third party that will decide in case of 
dispute.

This way, if ``participant 1'' and ``participant 2'' are honest, they will just agree on the result of the transaction 
and ``participant 3'' will not need to do anything. If ``participant 1'' and ``participant 2'' disagree, ``participant 
3'' will be able to choose whether the money must go to ``participant 1'' or to ``participant 2''.

In addition to this, in our implementation, the money paid for the item is 450 ADA, it must be committed by 
``participant 1'' before block 10, and it will be refunded to ``participant 1'' if there is no consensus before block 
90.

@@

\begin{haskellcode}
iCC1 :: IdentCC
iCC1 = IdentCC 1
\end{haskellcode}

And an identifier for the payment:

\begin{haskellcode}
iP1 :: IdentPay
iP1 = IdentPay 1
\end{haskellcode}

We can also create a sub-contract that allows the money to be redeemed by ``participant 1'':

\begin{haskellcode}
redeem_original :: Contract
redeem_original = RedeemCC iCC1 Null
\end{haskellcode}

Each participant has a say on who deserves the money: either ``participant 1'' deserves a refund, which we represent 
with the number $0$; or ``participant 2'' deserves a payment, which we represent with the number $1$. Because there is 
only one choice to make per participant, we use the same \haskellinline{IdentChoice} as their participant id. We can 
define a function that returns an observation that is true if and only if the participant \haskellinline{per} has 
chosen the number \haskellinline{c} as follows:

\begin{haskellcode}
chose :: Int -> ConcreteChoice -> Observation
chose per c = PersonChoseThis (IdentChoice per) per c
\end{haskellcode}

Then we can easily write a function that returns an observation that is true if and only if at least one of the 
participants \haskellinline{per} and \haskellinline{per'} has chosen the number \haskellinline{c} as follows:

\begin{haskellcode}
one_chose :: Person -> Person -> ConcreteChoice -> Observation
one_chose per per' val = (OrObs (chose per val) (chose per' val)) 
\end{haskellcode}

After that, we can write a function that returns an observation that is true if and only if at least 
two of the three participants \haskellinline{p1}, \haskellinline{p2}, and \haskellinline{p3} have chosen the number 
\haskellinline{c} as follows:

\begin{haskellcode}
two_chose :: Person -> Person -> Person -> ConcreteChoice -> Observation
two_chose p1 p2 p3 c = OrObs (AndObs (chose p1 c) (one_chose p2 p3 c))
                             (AndObs (chose p2 c) (chose p3 c))
\end{haskellcode}

Finally, we can write the escrow contract, which would remain as follows:

\begin{haskellcode}
escrow :: Contract
escrow = CommitCash iCC1 1 (ConstMoney 450) 10 100
                    (When (OrObs (two_chose 1 2 3 0)
                                 (two_chose 1 2 3 1))
                          90
                          (Choice (two_chose 1 2 3 1)
                                  (Pay iP1 1 2 (AvailableMoney iCC1) 100
                                       redeem_original)
                                  redeem_original)
                          redeem_original)
                    Null
\end{haskellcode}

The outermost primitive \haskellinline{CommitCash} allows the ``participant 1'' to commit 450 ADA before block 10, 
with the promise that money will be released on block 100 if they are not claimed before that.

The next primitive, \haskellinline{When}, waits for one of three things to happen:
\begin{enumerate}
 \item Two out of three choose $0$.
 \item Two out of three choose $1$.
 \item The block 90 is added to the blockchain.
\end{enumerate}

If the third option happens first, the money is refunded. Otherwise, there is a \haskellinline{Choice} that will 
immediately refund the money to ``participant 1'' unless two out of three chose $1$; in the later case, 
\haskellinline{Pay} will give ``participant 2'' the opportunity to claim the funds available in \haskellinline{iCC1} 
before block 100. If the funds are not claimed before block 100 they will also be refunded to ``participant 1''.

>>>>

This means that we require participants to commit money to cover all possible expenditure \emph{in advance of the contract executing}. In order to make sure that player continue to engage with a contract we ensure urgency by imposing timeouts: money is committed for a finite period, for example, and when waiting for a player to make a commitment we also impose a timeout to ensure that the contract does not become stuck even if one or more of the participants stops interacting with it. We revisit this example in Section~\ref{section:example-escrow} where we show how commitments, timeouts and other features of Marlowe are used to describe this as a self-enforcing contract ``on the blockchain''.

@@

In this section, we show how Marlowe can be used for designing a contract that incentivises saving. We use the 
following example: participant \haskellinline{2} offers 20 ADA to participant \haskellinline{1} in exchange for saving 100 ADA for 100 blocks. 
participant \haskellinline{1} will be able to withdraw the savings after block 20, but if that option is chosen, then participant 
 \haskellinline{2} will not pay the extra 20 ADA to participant \haskellinline{1}.

We will start from outer to inner primitives. The first thing is to allow participant \haskellinline{1} to commit the 100 ADA. The 
primitive says that with identity \haskellinline{IdentCC 1} (this is the identity of the commitment), participant 
\haskellinline{1} can commit \haskellinline{100} ADA before block \haskellinline{10}, and the commitment must 
expire on block \haskellinline{200}. But if the money is not committed before block \haskellinline{10}, then the 
contract will continue as \haskellinline{Null}.

@@

If the commitment is done correctly and on time, we continue as in \haskellinline{step2}. \haskellinline{step2} is 
another commitment, this time by participant \haskellinline{2}. The primitive says that with identity \haskellinline{IdentCC 2},
participant \haskellinline{2} can commit \haskellinline{20} ADA before block \haskellinline{20}, and the commitment
must expire on block \haskellinline{200}. But if the money is not committed before block \haskellinline{20}, then the
contract will continue as \haskellinline{RedeemCC (IdentCC 1) Null}, which in turn gives participant \haskellinline{1} the 
opportunity to withdraw all the money committed immediately.

@@

If the commitment is done correctly and on time, we continue as in \haskellinline{step3}. \haskellinline{step3}
waits until choice with identity \haskellinline{IdentChoice 1} is made by participant \haskellinline{1} or
until block \haskellinline{100} (whatever happens first). If the choice is made before block \haskellinline{100}, 
it continues as \haskellinline{stepRedeem}, if block \haskellinline{100} comes first, then it continues as 
\haskellinline{step4}.

@@

\haskellinline{step4} pays the \haskellinline{20} ADA committed by participant \haskellinline{2} in the commit with 
identity \haskellinline{IdentPay 1} to participant \haskellinline{1}, if the payment is claimed before block 
\haskellinline{200}. Once the payment is claimed or after block 200, it continues as \haskellinline{stepRedeem}.

@@

In this section, we revisit the escrow example that we discussed briefly in the introduction, and show  how we can make Marlowe contracts that are easier to write, read, and 
understand, by embedding them into Haskell code, taking advantage of the fact that Marlowe contracts are implemented as Haskell 
terms.

The example contract we use through this section implements an escrow contract. Let us imagine that participant \haskellinline{1} 
is buying some item from participant \haskellinline{2}. On one hand, if participant \haskellinline{1} pays before receiving the item, there 
is a risk that participant \haskellinline{2} will never give \haskellinline{1} the item. On the other hand, if participant \haskellinline{2} 
gives participant \haskellinline{1} the item before \haskellinline{1} pays, then there is a risk that \haskellinline{1} will never 
pay.

The escrow mechanism allows participant \haskellinline{1} to deposit the money into a contract, in a way that the money will only 
be released when two out of three participants agree on whether participant \haskellinline{2} has indeed given participant \haskellinline{1} 
the item. The third participant (participant \haskellinline{3}) is supposed to be a neutral third party that will decide in case of 
dispute.

This way, if participants \haskellinline{1} and \haskellinline{2} are honest, they will just agree on the result of the transaction 
and \haskellinline{3} will not need to do anything. If \haskellinline{1} and \haskellinline{2} disagree, participant \haskellinline{3} will be able to choose whether the money must go to \haskellinline{1} or to \haskellinline{2}.

In addition to this, in our implementation, the money paid for the item is 450 ADA, it must be committed by 
participant \haskellinline{1} before block \haskellinline{10}, and it will be refunded to participant \haskellinline{1} if there is no consensus before block 
\haskellinline{90}.

@@

\begin{haskellcode}
iCC1 :: IdentCC
iCC1 = IdentCC 1
\end{haskellcode}
And an identifier for the payment:
\begin{haskellcode}
iP1 :: IdentPay
iP1 = IdentPay 1
\end{haskellcode}
We can also create a sub-contract that allows the money to be redeemed by participant \haskellinline{1}:
\begin{haskellcode}
redeem_original :: Contract
redeem_original = RedeemCC iCC1 Null
\end{haskellcode}
Each participant has a say on who deserves the money: either participant \haskellinline{1} deserves a refund, which we represent 
with the number $0$; or participant \haskellinline{2} deserves a payment, which we represent with the number $1$. Because there is 
only one choice to make per participant, we use the same \haskellinline{IdentChoice} as their participant id. We can 
define a function that returns an observation that is true if and only if the participant \haskellinline{per} has 
chosen the number \haskellinline{c} as follows:
\begin{haskellcode}
chose :: Int -> ConcreteChoice -> Observation
chose per c = PersonChoseThis (IdentChoice per) per c
\end{haskellcode}
Then we can easily write a function that returns an observation that is true if and only if at least one of the 
participants \haskellinline{per} and \haskellinline{per'} has chosen the number \haskellinline{c} as follows:
\begin{haskellcode}
one_chose :: Person -> Person -> ConcreteChoice -> Observation
one_chose per per' val = (OrObs (chose per val) (chose per' val)) 
\end{haskellcode}
After that, we can write a function that returns an observation that is true if and only if at least 
two of the three participants \haskellinline{p1}, \haskellinline{p2}, and \haskellinline{p3} have chosen the number 
\haskellinline{c} as follows:
\begin{haskellcode}
two_chose :: Person -> Person -> Person -> ConcreteChoice -> Observation
two_chose p1 p2 p3 c = OrObs (AndObs (chose p1 c) (one_chose p2 p3 c))
                             (AndObs (chose p2 c) (chose p3 c))
\end{haskellcode}
Finally, we can write the escrow contract, thus:
\begin{haskellcode}
escrow :: Contract
escrow = CommitCash iCC1 1 (ConstMoney 450) 10 100
                    (When (OrObs (two_chose 1 2 3 0)
                                 (two_chose 1 2 3 1))
                          90
                          (Choice (two_chose 1 2 3 1)
                                  (Pay iP1 1 2 (AvailableMoney iCC1) 100
                                       redeem_original)
                                  redeem_original)
                          redeem_original)
                    Null
\end{haskellcode}

The outermost primitive \haskellinline{CommitCash} allows the participant \haskellinline{1} to commit 450 ADA before block 10, 
with the promise that money will be released on block 100 if they are not claimed before that.

The next primitive, \haskellinline{When}, waits for one of three things to happen:
\begin{enumerate}
 \item Two out of three choose $0$, for \haskellinline{pay}. 
 \item Two out of three choose $1$, for \haskellinline{refund}.
 \item The block 90 is added to the blockchain.
\end{enumerate}

If the third option happens first, the money is refunded. Otherwise, there is a \haskellinline{Choice} that will 
immediately refund the money to participant \haskellinline{1} unless two out of three chose option $1$; in the later case, 
\haskellinline{Pay} will give participant \haskellinline{2} the opportunity to claim the funds available in \haskellinline{iCC1} 
before block 100. If the funds are not claimed before block 100 they will also be refunded to participant \haskellinline{1}.
